### 2020-04-21 survival.tex
continunig with Cox

\fix{Need to add interpretation}

>>>>

We find that the average hazard ratios strongly correlate with
detailed nuances of the system cooling architecture.  The figures give
hazard ratios for each of the location variables, giving the ratio for
each level compared to its first (0) level (the 0 level is always
1). Due to the exponential nature of the CPH model, the horizontal
hazard ratio axis is on a log scale. The estimates include
uncertainty, which too is most reliably computed on a log scale (see,
for example, \cite{Ostrouchov88}).
